Exercise 1: Software Architecture Description of the HS07 System

### 2008-02-06 trunk/SAiP/Module1/H1/doc/paper.tex
Final updates from LKR

The major driving qualities attributes of the HS07 system
are\footnote{These qualities will be operationalized in Exercise 2}:

@@

Figure~\ref{fig:mv} shows the packages of the HS07 system, and how they interact 
with java packages used. The Sensor, Gateway and Actuator packages do not have
any knowledge of each other. They are all services that are able to respond to
HTTP queries. They uses the Invoker to interact with the other modules' HTTP
server. The interactions between the components are described in section
\ref{sec:component}. The Java packages Net, Jetty and Http are used for the
HTTP servers and HTTP requests.

@@

The sequence diagram illustrates the protocol of the interactions involved in the 
setup and the execution of the Gateway. It consists of a registration sequence and 
an infinite loop of retrieving the temperature of all registered themometers and 
notifying all observers (in this case the Radiators). The example is slightly 
simplified to improve readability, as the registerThermometer, registerObserver, 
getTemperature and notify is actually network calls performed using the Invoker and 
the respective servers.

@@

Figure~\ref{fig:allocation_pc} shows the setup as specified in the build-file
where all HS07 processes are located on the same node. As can be seen in the
figure the gateway can be accessed from one or more PC through an internet
connection.

@@

\begin{figure}[!htb]
\center {\includegraphics[viewport=110 200 600 420, scale=0.4]{figures/deployment_actual.pdf}}
\caption{HS07 Allocation Diagram showing deployment on seperate nodes}
\label{fig:allocation_actual}
\end{figure}

@@

\subsection{Not covered aspects}
%$<<$Are there aspects of the software architecture that have not been properly described?$>>$
\begin{description}
\item[Stakeholders and their concerns] This encompasses both users/aquirers and developers.
\item[Feasibility]
\item[Maintainablity]
\item[Security] How is the Gateway protected? What protection is there against attack and inproper use? 
\item[Safety] How is synchronization done? What insurances is there that the system cannot mailfunction and overheat a radiator or turn on a radiator which has been turned off deliberately because flammable material is placed near it?
\item[Availability] What is the up-time of the HTTP server that the system run on, both embedded and PC?
\item[Testability] What is the testability of the components? How easily is it to replace the actual HTTP servers with test doubles?
\end{description}

@@

This section describes how this architectural description conforms to recommended practice
that is defined in \cite{ieeerecommendedpractice}.

>>>>

The major driving quality attributes of the HS07 system
are\footnote{These qualities will be operationalized in Exercise 2}:

@@

Figure~\ref{fig:mv} shows the packages of the HS07 system, and how they depend
on java packages. The Sensor, Gateway and Actuator packages do not have
any knowledge of each other. They are all services that are able to respond to
HTTP queries. They use the Invoker to interact with the HTTP server in the
other modules. The interactions between the components are described in section
\ref{sec:component}. The Java packages Net, Jetty and Http are used for the
HTTP servers and HTTP requests.

@@

The sequence diagram illustrates the protocol of the interactions involved in the 
setup and the execution of the Gateway. It consists of a registration sequence and 
an infinite loop of retrieving the temperature of all registered themometers and 
notifying all observers (in this case the Radiators). The example is slightly 
simplified to improve readability, as the registerThermometer, registerObserver, 
getTemperature and notify is actually network calls performed using the Invoker and 
the respective servers. The figure shows an example with only one thermometer and
one radiator.

@@

Figure~\ref{fig:allocation_pc} shows an example setup
where all HS07 processes are located on the same node. As can be seen in the
figure the gateway can be accessed from one or more PCs through an internet
connection.

@@

\begin{figure}[!htb]
\center {\includegraphics[viewport=250 200 600 420, scale=0.4]{figures/deployment_actual.pdf}}
\caption{HS07 Allocation Diagram showing deployment on seperate nodes}
\label{fig:allocation_actual}
\end{figure}

@@

\subsection{Not covered aspects}
%$<<$Are there aspects of the software architecture that have not been properly described?$>>$
\begin{itemize}
\item \emph{Stakeholders and their concerns} This encompasses both users/aquirers and developers.
\item \emph{Feasibility}
\item \emph{Maintainablity}
\item \emph{Security} How is the Gateway protected? What protection is there against attack and inproper use? 
\item \emph{Safety} How is synchronization done? What insurances is there that the system cannot mailfunction and overheat a radiator or turn on a radiator which has been turned off deliberately because flammable material is placed near it?
\item \emph{Availability} What is the up-time of the HTTP server that the system run on, both embedded and PC?
\item \emph{Testability} What is the testability of the components? How easily is it to replace the actual HTTP servers with test doubles?
\end{itemize}

@@

This section describes how this architectural description conforms to the recommended practice
that is defined in \cite{ieeerecommendedpractice}.
